ML parameters

### 2022-11-21 workflow/notebooks/ml-params.Rmd
updated plots

```{r plot_dataset}
results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', metric == 'AUROC') %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('dataset')
```

## ML method - rf vs l2 logit

## metric - AUROC vs F1 score

>>>>

```{r plot_dataset}
results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', metric == 'AUROC') %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('dataset')

results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', metric == 'AUROC') %>% 
  ggplot(aes(perf_metric_value, dataset, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name')
```

## ML method - rf vs l2 logit
```{r plot_method}
results_dat %>% 
  filter(trainfrac == 0.8, metric == 'AUROC', dataset == 'full') %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('method')

results_dat %>% 
  filter(trainfrac == 0.8, metric == 'AUROC', dataset == 'full') %>% 
  ggplot(aes(perf_metric_value, method, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name')
```

## metric - AUROC vs F1 score
```{r plot_metric}
results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'full') %>% 
  ggplot(aes(perf_metric_value, perf_metric_name, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('metric')

results_dat %>% 
  filter(trainfrac == 0.8, method == 'glmnet', dataset == 'full') %>% 
  ggplot(aes(perf_metric_value, metric, color = outcome)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap('perf_metric_name')
```
